\begin{rubric}{Experience}
% \entry*[2014 -- $\cdots\cdot$]%
\entry*[Jun 2018 -- Jun 2020]%
	\textbf{Junior Software Tester,} Bhaktee Software Pvt. Ltd. (Rajkot), India
 
 \begin{enumerate}[noitemsep, topsep=0pt, left=-12em, labelwidth=12em]
     \item Debugging using Java and Python \textbullet{} Black box/white-box testing and test planning using Selenium \textbullet{} API testing using Postman  \textbullet{} reporting and tracking the errors in JIRA \textbullet{} Coding in HTML/CSS/JS and SQL by applying software development best practices.
     
     \item Leveraged AWS (CloudFormation, EKS) services and Docker \textbullet{} Participated in R\&D \textbullet{} Created CI/CD pipelines \textbullet{} Performed test-driven development \textbullet{} Used special methods for testing (TDD and BDD).

     \item Achieved a 20\% reduction in bugs by streamlining the testing process. Improved code performance by up to 30\% by identifying and resolving critical issues.
 \end{enumerate}
%
% Blank lines result in extra space!
%
\entry*[Jul 2020 -- Dec 2020]%
	\textbf{Software Developer Intern,} Hitech Transpower (Rajkot), India

  \begin{enumerate}[noitemsep, topsep=0pt, left=-12em, labelwidth=12em]
  \item Coded ML models (Python) \textbullet{} Front-end development (JS) \textbullet{} Back-end development (Python) \textbullet{} Database Management using SQL. 
  \item Optimized the front-end's code to reduce the response time by 10\% and DB query execution time by 5\%.
  \end{enumerate}
%
% Blank lines result in extra space!
%
\entry*[Jan 2021 -- Mar 2022]%
	\textbf{Software Developer,} Qtonz Infosoft (Rajkot), India

  \begin{enumerate}[noitemsep, topsep=0pt, left=-12em, labelwidth=12em]
  \item Android application development (Java) \textbullet{} Cross-functional team collaboration with tools like Jira and Azure DevOps. 
  \item Fostered collaboration among team members to adapt to changing requirements and efficiently deliver high-quality results \textbullet{} Implemented REST APIs and applied SOLID principles.
  \item Reduced development time by 25\% by using agile methodologies and efficient project management techniques \textbullet{} Received positive feedback from clients for delivering 3 high-quality applications before project deadlines.
  \end{enumerate}

\entry*[Oct 2022 -- Apr 2023]%
    \textbf{Service Assistant,} Concordia University (Montreal), Canada
 
 \begin{enumerate}[noitemsep, topsep=0pt, left=-12em, labelwidth=12em]
 \item Demonstrated proficiency in administrative tasks (data entry, file management, and document preparation) \textbullet{} Executed operations efficiently within the department. \textbullet{} Improved data management system resulting in a reduction in data entry errors. 
 \end{enumerate}

 \entry*[May 2022 -- Aug 2023]%
    \textbf{Junior Internal Auditor,} Concordia University (Montreal), Canada
 
 \begin{enumerate}[noitemsep, topsep=0pt, left=-12em, labelwidth=12em]
 \item Identified and managed risks for the company \textbullet{} Created audit plans to validate the expenses \textbullet{} Collected and analyzed data to find issues, and communicated findings to company leaders all while aiming for accuracy.
 \item Designed four new audit procedures that enhanced the efficiency and effectiveness of the audit process. 
 \end{enumerate}
%
\end{rubric}